---
title: "131_HW5"
author: "Zack Reardon"
date: "11/15/2022"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache.extra = rand_seed)
```

```{r, message=FALSE}
library(tidyverse)
library(tidymodels)
library(ggplot2)
library(glmnet)
# installing and loading janitor package
library(janitor)
tidymodels_prefer()

# uploading file to into R
pokemon <- read_csv("/Users/zackreardon/Downloads/homework-5/data/Pokemon.csv")
```

Exercise 1

```{r}
# show classes in pokemon data
sapply(pokemon, class)

# show portion of initial names in pokemon data
pokemon$Name %>%
  head()

# replace pokemon data with a clean_names version
pokemon <- clean_names(pokemon)

# show new classes after cleaning names in pokemon data
sapply(pokemon, class)

# show portion of new names in pokemon data
pokemon$name %>%
  head()
```
The class names in the data were converted to all lowercase letters, punctuation was removed, and the spaces were replaced with "_". This could be useful since it creates consistency when referencing class names when working with the dataset.

Exercise 2

```{r}
# creating a bar chart of variable type_1
ggplot(pokemon, aes(x=type_1)) + geom_bar()

# assessing number of classes of variable type_1
length(unique(pokemon$type_1))
```
There are 18 classes of the outcome `type_1`. Flying and fairy could be considered to have very few pokemon.

```{r}
# filter dataset to specific type_1
pokemon <- pokemon %>%
  subset(type_1=c(Bug, Fire, Grass, Normal, Water, Psychic))

# converting type_1 and legendary to factors
pokemon$type_1 <- as.factor(pokemon$type_1)
pokemon$legendary <- as.factor(pokemon$legendary)
```

Exercise 3

```{r}
# setting seed for repeatability
set.seed(100)

# performing initial split with 80% training, 20% testing and stratifying on type_1
pokemon_split <- initial_split(pokemon, prop=0.8, strata=type_1)

# assigning training and testing sets
pokemon_train <- training(pokemon_split)
pokemon_test <- testing(pokemon_split)

# verifying number of observations in training and testing sets
dim(pokemon_train)
dim(pokemon_test)
```
The training set has 639 observations while the testing set has 161 observations.

```{r}
# using v-fold cross validation on training set with 5 folds and stratifying on type_1
pokemon_folds <- vfold_cv(pokemon_train, v=5, strata=type_1)
```
Stratifying the folds might be useful since it would ensure that similar proportions of each primary type exist in each fold and allow for better comparisons between the predictability of each fold.

Exercise 4

```{r}
# creating recipe for relationship between predictor variables and response
pokemon_recipe <- recipe(type_1 ~ legendary + generation + sp_atk + attack + speed + defense + hp + sp_def, data=pokemon_train) %>%
  # dummy coding categorical predictors
  step_dummy(legendary, generation) %>%
  # centering and scaling all predictors
  step_center(all_predictors()) %>%
  step_scale(all_predictors())
```

Exercise 5

```{r}
# setting up elastic net model
en_spec <- multinom_reg(mixture=tune(), penalty=tune()) %>%
  set_mode("classification") %>%
  set_engine("glmnet")

# creating workflow
en_workflow <- workflow() %>%
  add_recipe(pokemon_recipe) %>%
  add_model(en_spec)

# creating grids for penalty and mixture
mixture_grid <- grid_regular(mixture(range=c(0,1)), levels=10)
penalty_grid <- grid_regular(penalty(range=c(-5,5)), levels=10)
```

Exercise 6

Exercise 7

Exercise 8
